\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.

In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries. FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions. %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains. FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions. The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions. Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.

@@

\medskip
Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

\begin{equation}
Ca = \frac{\mu U}{T}
\label{eq:capillary_number}
\end{equation}

@@

\medskip
Fluid $1$ is introduced from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used). 
%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$. %\ref{fig:square}b).

@@

\medskip
In this section three different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a},\ref{fig:6b},\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

@@

\medskip
Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations. In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.

@@

\medskip
Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet. A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected. What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}). The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh. For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$. %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. 
Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c} and \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described. In this set the interfacial instability is becoming more profound as the flow develops. Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.

@@

\medskip
Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields (see Fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$. Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).

The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$. Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.

@@

Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.

This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude. Viscocity is a measure of resistance, therefore a frictional property. In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface. For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted. Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$. Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers. In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers. In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse. This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs. The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.

>>>>

\medskip
Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.

\medskip
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

\medskip
The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries. FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions. %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains. FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions. The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions. Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.

@@

\medskip
Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. \citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
T is the surface tension and U is a velocity characteristic of the moving interface.

\begin{equation}
N_{C} = \frac{\mu U}{T}
\label{eq:capillary_number}
\end{equation}

@@

\medskip
Fluid $1$ is introduced from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used). 
%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
A domain consisting of $4$ square regions in which each quarter is represented by a permeability value %(Fig.\ref{fig:square}a) 
and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$. %\ref{fig:square}b).

@@

\medskip
In this section three different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

@@

\medskip
Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3} 
\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations. In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.

@@

\medskip
Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet. A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected. What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude. %(fig.\ref{fig:1testcase})
The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh. For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$. %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used. 
Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
-\ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described. In this set the interfacial instability is becoming more profound as the flow develops. Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived. Fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.

@@

\medskip
Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2}) 
as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$, 
%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes). The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$. Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.

@@

\medskip
Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.

\medskip
This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude. Viscocity is a measure of resistance, therefore a frictional property. In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface. For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted. Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$. Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers. In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers. In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse. This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs. The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.

### 2017-05-25 Papers/ViscousInstabilities/article_table.tex
cleaning the paper adding some extra info

\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. REPLACE ALL XX; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
\end{table}

>>>>

\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results_homo_hete}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. REPLACE ALL XX; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
\end{table}
